---
title: "MTA Casino Revenue"
subtitle: "Initial Analysis"
author: "Don Boyd"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
format:
  typst:
    toc: false
execute:
  eval: true
  echo: false
  output: false
---

```{=typst}
#set page(margin: 1in)
#set text(size: 11pt)
```
## Highlights

```{=typst}
#v(1em)
```
-   New York State's [Gaming Facility Location Board](https://nycasinos.ny.gov/) seems highly likely to approve 3 new casino licenses by December 1, 2025 and license the winners by December 31, 2025.

-   All 3 will be in New York City outside Manhattan. See table below.

-   License fee and tax revenue will depend upon structures agreed upon by the GFLB and each casino, separately. The statute sets out minimum requirements:

-

    ```
    One-time license fee of at least $500 million per casino
    ```

-

    ```
    Ongoing revenue at tax rates of at least 25% for
    ```

```{r}

library(tinytable)
library(tidyverse)

casino_data <- read_delim(
  file = "
applicant; location; proposed_license; proposed_rates; key_features
Resorts World (Genting); Queens; \\$600m; 56\\% slots, 30\\% tables; stuff
Metropolitan Park; Queens; >=\\$500m; Not published; stuff2
Bally's Bronx	Bronx; ≥\\$500 million; Not published;Green space, robust community commitments; more stuff
",
  delim = ";",
  trim_ws = TRUE,
  show_col_types = FALSE
)

# casino_data
casino_data

```

```{=typst}
#v(1em)
```
```{r}
#| label: show-casinos-table
#| output: true

tt(casino_data) |>
  style_tt(align = "lllll")

```

## Background